### 2017-06-06 Paper.tex
Small change in writeup

	Since it is a new model of uncertainty, we first formally describe the crashing optimization problem with disruptions. Given the limited number of disruption occurrence, the problem can be formulated as a stochastic mixed integer program and we will present the extensive formulation in Section~\ref{sec:formulation}. The large scale and the discrete non-convex nature of the extended formulation means it may not be solved efficiently to desirable tolerance level. In Section~\ref{sec:decomposition}, a branch-and-bound method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption. We show such a decomposition method will solve the integer program to the exactness within finite number of iterations. \\

@@

\section{Problem Formulation} \label{sec:formulation}
	\begin{itemize}
		\item Static PERT problem formulation/ Stochastic PERT literature review: simulation optimization/ Distributionally robust: Natarajan
		\item Assumptions: not affected by the disruption once started.
	\end{itemize}
	Suppose at most one stochastic disruption will occur in the entire project span. When the disruption happens is a random variable, of which the distribution is known to us. The stochastic disruption

>>>>

	We first formally describe the crashing optimization problem with disruptions. Given the limited number of disruption occurrence, the problem can be formulated as a stochastic mixed integer program and we will present the extensive formulation in Section~\ref{sec:formulation}. The large scale and the discrete non-convex nature of the extended formulation means it may not be solved efficiently to desirable tolerance level. In Section~\ref{sec:decomposition}, a branch-and-bound method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption. We show such a decomposition method will solve the integer program to the exactness within finite number of iterations. \\

@@

\section{Problem Formulation} \label{sec:formulation}
	\begin{itemize}
		\item Static PERT problem formulation/ Stochastic PERT literature review: simulation optimization/ Distributionally robust: Natarajan
		\item Assumptions: not affected by the disruption once started.
	\end{itemize}
	\textcolor{blue}{list the literature of static PERT}
